Lawrence Bull, PhD

### 2023-02-22 index.qmd
update links in index

---
title: "Lawrence Bull, PhD"
about:
  template: solana
  image: images/mugshot.png
  links:
    - text: github
      href: https://github.com/labull
    - text: google scholar
      href: https://scholar.google.com/citations?user=Lszt1B4AAAAJ&hl=en
    - text: research gate
      href: https://www.researchgate.net/profile/Lawrence-Bull-2
    - text: orcid
      href: https://orcid.org/0000-0002-0225-5010
    - text: twitter
      href: https://twitter.com/lwrncebull?lang=ar
---

@@

I'm particularly interested in _multilevel structures_ that appear in measurements from populations of systems -- trains, [planes](), [automobiles](https://doi.org/10.48550/arXiv.2204.12404) (... [wind turbines](https://arxiv.org/abs/2111.15496)).
By encoding domain expertise in a Bayesian workflow, complex models can be built from interpretable units, allowing machines to share information and increasing the value of data.
At the population level, alternative insights can emerge that might otherwise be missed -- the whole is something _besides_ its parts.

@@

>>>>

---
title: "Lawrence Bull, PhD"
about:
  template: solana
  image: images/mugshot.png
---

@@

I'm particularly interested in _multilevel structures_ that appear in measurements from populations of systems -- trains, [planes](https://www.sciencedirect.com/science/article/pii/S0022460X21001449), [automobiles](https://doi.org/10.48550/arXiv.2204.12404) (... [wind turbines](https://arxiv.org/abs/2111.15496)).
By encoding domain expertise in a Bayesian workflow, complex models can be built from interpretable units, allowing machines to share information and increasing the value of data.
At the population level, alternative insights can emerge that might otherwise be missed -- the whole is something _besides_ its parts.

@@

<div style="text-align: right">

[github](https://github.com/labull)

[google scholar](https://scholar.google.com/citations?user=Lszt1B4AAAAJ&hl=en)

[research gate](https://www.researchgate.net/profile/Lawrence-Bull-2)

[orcid](https://orcid.org/0000-0002-0225-5010)

[twitter](https://twitter.com/lwrncebull?lang=ar)
